%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Zack Pollard} % Your name
\address{github.com/zackpollard \\ git.zackpollard.pro} % Your address
\address{Mobile: 07928015705 \\ Email: z.r.e.pollard-14@student.lboro.ac.uk} % Your secondary addess (optional)
\address{1 The Pyghtle, Westoning, MK45 5LJ} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin {rSection}{Profile}

A Loughborough University graduate with a 1st class BSc in Computer Science and 1-year experience as an intern at IBM iX, the worlds largest digital agency. Systems Administrator and Programmer with 9 years of experience, through both freelance work and employment. Primarily works using Java with varied experience in other languages including C++, Python and Node.JS. Excited about learning more in this continually changing industry.

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\begin{rSubsection}{Loughborough University}{September 2014 - July 2018}{Bachelor of Science in Computer Science (1st Class)}{Loughborough, Leicestershire}
Dissertation: Secure Smart Lock System
\end{rSubsection}

\begin{rSubsection}{Harlington Upper School}{September 2009 - July 2014}{GCSE and Sixth Form}{Harlington, Bedfordshire}
\item \textbf{A Levels: } Mathematics (A), Physics (B), ICT (C)
\item \textbf{Level 3 BTECs: } Subsidiary Diploma in Sport (Distinction*)
\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}
	
\begin{rSubsection}{IBM - iX Studios London}{July 2016 - November 2016}{Interactive Developer}{Southbank, London}
	\item Received the top performance rating during placement, awarded to only 10\% of interns, allowing application back to IBM without interview as a graduate.
	\item Working directly with clients from Deutsche Bank and BP.
	\item \textbf{Deutsche Bank:}\\
	- Built a custom development pipeline using Jenkins 2.0 for the Deutsche Bank teams paving the way to increased productivity and automation.\\
	- Onboarded a new team onto the Deutsche Bank project whilst operating as the technical lead on-site for IBM.
	\item \textbf{BP}\\
	- Worked within an agile team, both local and remote to produce a premium B2C Android application released globally.\\
	- Designed and implemented a custom solution for making a single Android application for multiple different markets with the same source code.\\
	- Reinvented the devops flow using Jenkins pipelines to automate adding new modules, source code merging, releases, unit testing and more, along with feedback in case of code issues.\\
	- Wrote dynamic view generation code for Android, allowing us to create receipts populated by each module individually so we didn't need unique receipts code for every country.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Woodlands Middle School}{July 2011 and July 2012}{Assistant Systems and Network Technician}{Flitwick, Bedfordshire}
	\item Provided technical support to users in a clear and concise manner.
	\item Kept to a schedule and completed jobs within required deadlines.
	\item Problem solving under pressure in time-sensitive situations.
	\item Worked effectively with members of a team to coordinate network repair tasks in order to prevent interference with users on the network.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Freelancing}{2009 - Present}{Java Development and Systems Administration}{}
\item Dealing with clients requirements on a daily basis.
\item Managing time and providing accurate time frames for completion of projects.
\item Working as part of a team on projects utilising git for version control.
\item Persevering with problems to find acceptable solutions.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	KEY SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSectionList}{Key Skills}
\item \textbf{Problem Solving:}
Used extensively during my time at IBM, one example was when we needed to re-write the Android application to work in different countries with some code being slightly different. We worked on building a custom solution so that we could have individual modules that could be put into any application, and the code would adapt itself based on what modules were loaded when the application started up.

\item \textbf{Communication:} 
During my time at IBM I worked with clients on and off-site, as well as having to communicate effectively with remote teams during stand-ups and throughout the day. During my freelance work, I had to continually communicate with remote clients to keep them up to date with progress and establish requirements.

\item \textbf{Teamwork:}
Demonstrated throughout my time at IBM, specifically due to working in small agile teams on both the Deutsche Bank and BP projects. Whilst on the Deutsche Bank project I was given the opportunity to be the technical lead, part of which involved onboarding a new team.
\end{rSectionList}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}
	
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages 	& Java, C++, Python, Lua, HTML, CSS, PHP, JavaScript, Node.JS, Groovy \\
Data Structures & XML, JSON, YAML \\
Databases & MySQL, PostgreSQL, MongoDB \\
Tools 	& Git, Vim, Bash, Maven, Jenkins, LaTeX, KVM, SSH, VNC, JIRA, Docker,\\
		& Google Cloud, IBM Bluemix, RxJava, Retrofit \\
Operating Systems 	& CentOS 6/7 (Redhat), Debian, Arch (Arch), UnRAID, Cisco IOS
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXTRA QUALIFICATIONS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Additional Qualifications}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Saxophone & ABRSM Grade 8 \\
Piano & ABRSM Grade 6 \\
Music Theory & ABRSM Grade 5 \\
Kayaking \& Canoeing & Canoe England BCU 2 Star \\
Full UK Clean Driving Licence
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	HOBBIES AND INTERESTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSectionList}{Hobbies and Interests}
	
\item Played the Saxophone and Piano for 13 and 15 years respectively.
\item Participated in various bands throughout Middle and Upper School, as well as playing in the University Jazz band, Tuxedo Swing.
\item Kayaking, Canoeing, Mountain Biking and Rock Climbing for 8 years.

\end{rSectionList}
 
\begin{rSection}{References}

Available upon request.

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
